%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, letterpaper]{article} % Document font size and paper size

\usepackage{fontspec} % Allows the use of OpenType fonts

\usepackage{geometry} % Allows the configuration of document margins
\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\leavevmode\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\renewcommand*{\marginfont}{\sffamily}
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Wang Liao - vita},pdfauthor={Wang Liao}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors


% Wang's additional modification
\usepackage{fancyhdr}

\usepackage{multicol}
\usepackage{academicons, fontawesome}
\usepackage{hanging}

\usepackage[parfill]{parskip}


\pagestyle{fancy}
\fancyhf{}
\rhead{\textsf{Wang Liao | CV - Page \thepage}}
\renewcommand{\headrulewidth}{0pt}

% \usepackage{titlesec}
% \titlespacing*{\section}{0pt}{20pt plus 0pt minus 0pt}{10pt plus 0pt minus 0pt}


%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
% \setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
% %\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
% \sectionfont{\mdseries\upshape\Large} % Set font options for sections
% \subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
% \subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
% \chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Times} % Main text font
\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
\newcommand{\amper}{{\fontspec[Scale=.95]{Times}\selectfont\itshape\&}} % Custom ampersand character
\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
\subsectionfont{\sffamily\mdseries\normalsize} % Set font options for subsections
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}
% \setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------
\thispagestyle{empty}

\begin{multicols}{2}
[
{\LARGE Wang Liao} % Your name
]
PhD Candidate\\
Department of Communication\\
455 Mann Library Building\\ % Your address
Cornell University\\
Ithaca, NY \texttt{14850}\\
% USA\\[.2cm]

\columnbreak
{\tiny \faicon{phone}} 607-379-3240\\ % Your phone number
{\tiny \faicon{envelope-o}} \href{mailto:wl483@cornell.edu}{wl483@cornell.edu}\\ % Your email address
% Fax: \texttt{609-924-8399}\\[.2cm] % Your fax number
% {\tiny \aiicon{googlescholar}} \href{https://scholar.google.com/citations?user=dH4uqKsAAAAJ}{scholar.google.com/citations?user=dh4uqksaaaaj}\\
% {\tiny \aiicon{orcid}} \href{http://orcid.org/0000-0001-6192-0837}{orcid.org/0000-0001-6192-0837}\\
% {\tiny \aiicon{researchgate}} \href{https://www.researchgate.net/profile/Wang_Liao}{researchgate.net/profile}\\
{\tiny \faicon{user}} \href{https://wliao229.github.io}{wliao229.github.io}\\ % Your academic/personal website

\end{multicols}
% \vfill % Whitespace between contact information and specific CV information

%------------------------------------------------

% \section*{Current position}

%------------------------------------------------

\section*{Areas of Research Interest}

Communication in Multilevel Social Processes (Interpersonal, Group, and Orgnizational)\\
Medium Effects and Communication Technologies\\
Relational and Group Processes\\  
Social and Communication Networks\\ 
Social Functionality of Affect and Emotion\\ 
Quantitative Methods % Your primary areas of research interest

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \section*{Appointments held}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section*{Education}

PhD in Communication (expected, 2018 summer) \\
    \textsf{
        Department of Communication, Cornell University\\
        Advisory Committee: Connie Yuan (chair), Drew Margolin, Ed Lawler, Michael Macy\\
        Mentor: Felix Thoemmes, Natalie Bazarova
        % Dissertation: Communication, affect, and status organizing in task-oriented groups
            } 

MS in Communication \years{2015} \\
    \textsf{Department of Communication, Cornell University}

MA in New Media Studies \years{2012} \\
    \textsf{School of Journalism and Communication, Tsinghua University, China}

BA in Advertising \years{2009} \\
    \textsf{Department of Advertising, Xiamen University, China}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%----------------------------------------------------------------------------------------

\section*{Journal Articiles}

\begin{hangparas}{.25in}{1}
    
    \textbf{Liao, W.}, McComas, K. A., \& Yuan, Y. C. (2017). \years{2017} The influence of unrestricted information exchange on willingness to share information with outsiders. \textsl{Human Communication Research, 43}, 256–275. \href{http://doi.org/10.1111/hcre.12104}{doi:10.1111/hcre.12104}  

    Thoemmes, F., \textbf{Liao, W.}, \& Jin, Z. (2017). The analysis of the regression-discontinuity design in R. \textsl{Journal of Educational and Behavioral Statistics, 42}, 341-360. \href{http://doi.org/10.3102/1076998616680587}{doi:10.3102/\\1076998616680587} 

    \textbf{Liao, W.}, Bazarova, N. N., \& Yuan, Y. C. (2016). \years{2016} Expertise judgment and communication accommodation in linguistic styles in computer-mediated and face-to-face groups. \textsl{Communication Research}. Advance online publication. \href{http://doi.org/10.1177/0093650215626974}{doi:10.1177/0093650215626974}

    \textbf{Liao, W.}, Yuan, Y. C., \& McComas, K. A. (2016). Communal risk information sharing: motivations behind voluntary information sharing for reducing interdependent risks in a community. \textsl{Communication Research}. Advance online publication. \href{http://doi.org/10.1177/0093650215626981}{doi:10.1177/\\0093650215626981}

    \vspace{\parskip}
\end{hangparas} 

%------------------------------------------------

\subsection*{manuscripts under review}

\begin{hangparas}{.25in}{1}

    \textbf{Liao, W.}, Bazarova, N. N., \& Yuan, Y. C. Unpacking medium effects: Using the social relations model to study social psychological aspects of in computer-mediated communication. \textsl{(revise \& resubmit)}

    Margolin, D. \& \textbf{Liao, W.}~Emotional ‘group talk’: A communication logic for self-organized solidarity among national football league fans on Twitter. \textsl{(under review)}

    Yuan, Y. C., \textbf{Liao, W.}, \& Bazarova, N. N. Judging expertise through communication styles in intercultural collaboration \textsl{(under review)}

    \vspace{\parskip}

\end{hangparas}
\vspace{+\parskip}
%------------------------------------------------

\section*{Book Chapter}
\begin{hangparas}{.25in}{1}

    \textbf{Liao, W.}, \years{2016}  MacDonald, P., \& Yuan, Y. C. (2016). The impact of communication behaviors on expertise recognition in intercultural collaboration. In J. Treem \& P. Leonardi (Eds.), Communication, Expertise, and Organizing. Oxford, UK: Oxford University Press

    \vspace{\parskip}

\end{hangparas}

%------------------------------------------------

\section*{Conference Presentations / Proceedings}
\begin{hangparas}{.25in}{1}

    \textbf{Liao, W.}, \years{2017} Bazarova, N. N., \& Yuan, Y. C. (2017, May). Development and application of an analytical framework for analyzing social behaviors with social relations models in CMC Groups. Poster presented at the 67th Annual Conference of the International Commmunication Association, San Diego, CA, USA

    \textbf{Liao, W.}, \years{2016} McComas, K. A., \& Yuan, Y. C. (2016, November). The influence of unrestricted information exchange on willingness to share risk information with outsiders. Paper presented at the National Communication Association 102th Annual Convention, Philadelphia, PA, USA

    Margolin, D., \years{2015} \textbf{Liao, W.}, \& Lin, Y.-R. (2015). Conversing in reflective glory: A systematic study using national Football League games. Proceedings of ICWSM’15

    \textbf{Liao, W.}, Bazarova, N. N., \& Yuan, Y. C. (2015, May). Expertise judgment and communication accommodation in CMC and FtF groups. Paper presented at the 65th Annual Conference of the International Communication Association, San Juan, Puerto Rico

    \textbf{Liao, W.}, Yuan, Y. C., \& McComas, K. A. (2015, August). Communal risk information sharing: motivations behind voluntary information sharing of late blight infection in U.S. agricultural communities. \textsl{Top 2 faculty paper of the CommSHER division} at the Annual Conference of the Association for Education in Journalism and Mass communication, San Francisco, CA, USA

    \textbf{Liao, W.} \years{2012-2014}\& Liu, Y. (2014, May). Personalized public goods production in social networking site. Paper presented at the 63th Annual Conference of the International Communication Association, Seattle, WA, USA

    Theommes, F. \& \textbf{Liao, W.} (2014, May). The Markov equivalence class of the mediation model. Paper presented at the Modern Modeling Method Conference. Storrs, CT, USA

    \textbf{Liao, W.} \& Liu, Y. (2014, May). Personalized public goods production in social networking site. Paper presented at the 63th Annual Conference of the International Communication Association, Seattle, WA, USA

    \textbf{Liao, W.} (2013, Nov). The digital legitimation of stratification. National Communication Association 99th Annual Convention, Washington, D.C., USA

    Thoemmes, F. \& \textbf{Liao, W.} (2013, May). Propensity score matching (with multilevel data) using SPSS and R. Paper presented at the Modern Modeling Methods Conference, Storrs, CT, USA

    \vspace{\parskip}
    
\end{hangparas}

%----------------------------------------------------------------------------------------
%   COMPUTER PROGRAMS
%----------------------------------------------------------------------------------------

\section*{Computer Programs}

R Package for Regression Discontinuity Designs \years{2015-} \\
\textsf{
    with Dr. Thoemmes, F. \& Jin, Z.
}

SPSS Plugin for Propensity Score matching \years{2013-2015} \\
\textsf{with Dr. Thoemmes, F. \\
\href{http://sourceforge.net/projects/psmspss/}{sourceforge.net}}


%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------

\section*{Teaching Experience}

Structural Equation Modeling (COMM 6950) \years{2016 Spring} \\
\textsf{
Department of Communication, Cornell University\\
Co-Instructor (6 students): lecturing for lab sessions and recent advances in SEM 
}

Research Issues in Social Networks (INFO 7040) \years{2013 Fall} \\
\textsf{
Department of Information Science, Cornell University\\
Teaching Assistant (20 students): grading essays for first-year graduate students in Information Science }

%----------------------------------------------------------------------------------------
%   GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\section*{Honors \& Awards}

Anson Rowe Advanced Student Award \years{2016} \\ 
\textsf{Cornell University} \\

Top faculty paper (2nd place) \years{2015} \\
\textsf{CommSHER Division, AEJMC}

%----------------------------------------------------------------------------------------
%   FUNDED RESEARCH SECTION
%----------------------------------------------------------------------------------------

\section*{Experience in Grant-based Research}

Web-based \years{2015-} Software to Estimate Power and Causal Effects of Various Regression Discontinuity Designs (US Department of Education, Institute of Education Sciences, R305D150029)  \\
\textsf{
PI: Felix Thoemmes\\
Role: research assistant (collaborating on the design and implementation of the method and software)\\
Output (current): coauthoring a paper published in \textsl{Journal of Educational and Behavioral Statistics}
}

Reducing \years{2013-2015} Losses to Potato and Tomato Late Blight by Monitoring Pathogen Populations, Improved Resistant Plants, Education, and Extension (US Department of Agriculture, National Institute of Food and Agriculture, 2011-68004-30154) \\
\textsf{
PI: Katherine McComas\\
Role: research assistant (leading a national survey of risk information sharing among US growers)\\
Output: leading two papers published in \textsl{Communication Research} and \textsl{Human Communication Research}
}

\section*{Skills in Applied Statistics}

Multilevel Modeling, Structural Equation Modeling, Panel Data/Fixed-Effects Modeling, Statistical Network Analyses, Causal Inference in Observational Data.

%------------------------------------------------

\section*{Services}

Job Search Commitee \years{2016} \\
\textsf{Dept. of Communication, Cornell University}

%------------------------------------------------

\section*{Professional Affiliations}

National Communication Association, Member\\
International Communication Association, Member\\
Association for Education in Journalism and Mass Communication, Member.
% ...

\vfill{} % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

\begin{center}
{\scriptsize Last updated: \today\- •\- \href{https://wliao229.github.io}{wliao229.github.io}} % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
\end{center}

%----------------------------------------------------------------------------------------

\end{document}